The prime of their life - the halflife of acting talent

### 2017-08-30 01_actor_careers/05_report.Rmd
mapper

chart_data = 
  known_summary %>%
  union_all(unknown_summary) %>%
  group_by(role_type) %>%
  mutate(
    films_prop = films / sum(films),
    people_prop = distinct_people / sum(distinct_people)
  ) %>% ungroup()

map(c("Actor", "Director", "Director (Non Top250)"), function(x) {

    chart_data %>%
    filter(role_type == x) %>%
    gather("variable", "value", films_prop, people_prop) %>%
    hchart(hcaes(x = gender, group = variable, y = value)) %>%
    hc_title(text = x)

}) %>%
hw_grid(ncol = 1) %>% 
browsable()

>>>>

chart_data = 
  known_summary %>%
  union_all(unknown_summary) %>%
  filter(!is.na(gender))

map(c("films", "distinct_people"), function(x) {

    data = 
      chart_data %>%
      select_("role_type", "gender", x) %>%
      spread_("gender", x, fill = 0)

    base = highchart() %>%
            hc_chart(type = "column") %>%
            hc_add_theme(tmbish) %>%
            hc_xAxis(categories = data$role_type) %>%
            hc_plotOptions(
              column = list(
                stacking = 'percent',
                dataLabels = list(
                  enabled = TRUE
                  #,formatter = JS("function(){ return(point.percentage)}")
                )
              )
            ) %>%
            hc_title(text = ifelse(x=="films", "By Volume of Films", "By Distinct Individuals"))

    for (i in c("female", "male")) {
      base = base %>% hc_add_series(name = i, data = data[,i] %>% unlist() %>% as.integer())
    }

    if (x == "films") { base  = base %>% hc_legend(enabled=FALSE)}

    return(base)

}) %>%
hw_grid(ncol = 2) %>% 
browsable()
